### 2025-03-30 rebuttal.md

We can include the training times in the paper. However, it should be noted that the performance also depends heavily on some parameters such as training epochs for value, policy (and, reward and world model for SHAC++). Therefore, this would not be indicative on what method is the fastest to train. Nonetheless, SHAC++ is definitely more computationally heavy this is because it needs to train the reward and world model in addition to what SHAC does. 
However, for a comparison consider that for the sampling environment (which is the slowest in VMAS) SHAC++ takes 16 hours to complete the 20000 episodes similarly to PPO, while SHAC takes about 10 hours.

# Reviewer 2

> problematic claims that are misaligned with each other and with the supporting evidence.

We apologize for the confusion. We'll revise the introduction to clarify our goals. SHAC demonstrated excellent performance in single-agent, differentiable settings. Our work aims to lift these constraints by developing SHAC++, which handles multi-agent and non-differentiable environments while maintaining comparable performance to SHAC.

@@

> lower performance in some cases

**Goal**: Lift SHAC's requirements to broaden its applicability---see previous point.

**Skewed results**: In VMAS, agents only access local observations. SHAC++ respects this limitation while SHAC accesses global state through its gradients, giving SHAC an advantage. Despite this, both algorithms perform similarly.

@@

**Early stopping** We also note that as soon as a run achieves the 90% of the maximum reward, we stop the training, this can lead to some variance in the final performance.

> The proposed method is not evaluated in such complex environments; the test environments are very simple

While these environments present significant challenges for PPO/MAPPO (as shown by their poor performance), we acknowledge they could be more complex. We'll revise our paper to better reflect this and explain our environmental choices in the discussion section.

> The performance of SHAC++ is questionable in more complex MARL

We understand that more complex environments may offer more challenging scenarios. However, we want to stress that these environments are already incapacitating for PPO/MAPPO. 
We plan to evaluate SHAC++ in more complex environments with larger agent populations in the next revision. We would appreciate the reviewer's suggestions for suitable differentiable, scalable multi-agent environments that could provide more comprehensive benchmarks.

> Numerous practical algorithms already exist for such environments, for example MAPPO, HAPPO, and QMIX in multi-agent scenarios

**PPO & MAPPO confusion**: We always use MAPPO where PPO is evaluated for multi-agent setting (we just briefly mention in the paper). We will fix this in the paper.

**Why MAPPO and not others**: While HAPPO and QMIX are valid candidates, we limited baselines to maintain statistical significance. HAPPO's non-homogeneous design (non-shared parameters between agents) makes it computationally expensive and creates an unfair comparison. In our experiments, we consistently use parameter sharing for scalability. MAPPO supports both shared and non-shared parameters, making it appropriate for our evaluation.

@@

**Why not SAC**: We appreciate the author suggestion to include SAC and we will consider adding it to the baselines for the next revision. However, the original SHAC paper already included a SAC baseline. Ultimately, we believe that the inclusion of SAC would not add much to the main discussion.

**Why not other algorithms**: We excluded PODS, CE-APG, and BPTT as they are precursors to SHAC. SAM-RL requires a differentiable renderer beyond the differentiable environment, making it even less practical (though our framework could learn this component too). DiffTORI's test-time optimization approach is difficult to extend to multi-agent settings. AHAC addresses stiff dynamics by truncating trajectories, which could improve SHAC's performance but doesn't address its fundamental limitations.

> The authors estimate the reward function and state transition using only local agent states and actions as input. This approach may limit the method's generality and correctness

@@

Yes, this is intentional for realistic, partially observable environments. SHAC++ can use local information, unlike SHAC (needing global state). We prioritize this realism (details in paper).

> The parameters for the policy, value, reward, and state transition networks are all denoted by $\theta$

This is intentional, providing flexibility. Parameters can be fully separate ($\theta=[\theta_{\text{policy}}, \theta_{\text{reward}}, \theta_{\text{value}}, \theta_{\text{world}}]$) or have varying degrees of sharing.

> modeling the environment instead of directly utilizing its information might introduce biases and lead to performance degradation

We agree that learned models introduce potential for inaccuracy. Policy performance depends on model quality - accurate models provide informative gradients, while inaccurate ones introduce noise. However, we can mitigate this by bootstrapping the world model using existing trajectories before policy training, improving stability.

@@

> To what SHAC+ stands for?

SHAC+ refers to a variant where only the reward function is learned while using the true environment dynamics.

> Visual analysis of the trained policies' behavior would be more convincing

@@

We will include snapshot from trajectories from the learned policy.

> Confusion on $l$ and $r$

$l$ and $r$ are the lower and upper bounds of the action space (e.g., for actions in range (0,1), $l=0$ and $r=1$).
